\documentclass{novelette}
% What, no settings? Using defaults here!
\mode{align} % Choices: draft shade align final
\begin{document}
\begin{opening}
\null\null\null\null\null\null
\name{1}
\desc{The Storm}
\null\null\null\null\null
\end{opening}
\init{I}{t was a dark and stormy night.} Lord Withens rode through the gloom,
which is how things usually are, in situations where it is dark and stormy.
Maybe things are different where you are. For example, if you live in
Trondheim, and it is June, the nights are not very dark. Not sure if they
are stormy. But this is not Trondheim.

As he rode through the darkness, Lord Withens thought to himself,
``My, this night is stormy.''

But the darkness and storminess would be just the beginning of his troubles.
His destination was the castle of Lady Withens, who was rather pleasant,
but a book like this needs trouble somewhere along the line, eh? It also
needs a car chase near the ending, if the author has any hopes of this
becoming a major motion picture. Don't worry, the car chase comes later.

At this point is should be mentioned that Lord Withens was married to Lady
Withens, and Lady Withens was married to Lord Withens. But they were not
the same lords and ladies. You see, Withenshire was a rather remote area,
where over the course of centuries everyone was everyone else's relative,
to a greater or lesser degree, most of them were named Withens, and most
of them were lords or ladies. So, if you have been following closely,
by now you realize that this particular lord was cheating on his lady,
and this particular lady was cheating on her lord.

Without that kind of complication, we wouldn't have much of a story,
now would we? At any rate, all the lords and ladies drove very expensive
sports cars, so we can look forward to one heck of a chase scene.



\end{document}
